%-------------------------
% Resume in Latex
% Author
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{--}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm,label={}]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{MD Mokaddimul Kabir} % Your Name
\newcommand{\course}{Computer Science} % Your Program
\newcommand{\roll}{N/A} % Your Roll No.
\newcommand{\phone}{+8801795019802} % Your Phone Number
\newcommand{\emaila}{riadkabir45@gmail.com} %Email 1

\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------

{
\begin{tabularx}{\linewidth}{L r} \\
  	\textbf{\Large \name} & {\raisebox{0.0\height}{\footnotesize \faPhone}\ \phone}\\
  Computer Science Student & \href{https://github.com/riadkabir45}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {riadkabir45}} \\  
  {Brac University} & \href{https://linkedin.com/in/mokaddimul-kabir}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {mokaddimul-kabir}}
\end{tabularx}
}


%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Brac University | Bachelor's Degree (Current)}{CGPA: 3.31 (Ongoing 99/124 credit)}
      {Major: Computer Science}{Dhaka, Bangladesh}
    \resumeSubheading
      {Chuadanga Govt College | HSC (2020-2021)}{GPA: 5.00}
      {Subject: Science}{Chuadanga, Bangladesh}
    \resumeSubheading
      {Victoria Jubilee Government High School | SSC (2018)}{GPA: 4.78}
      {Subject: Science}{Chuadanga, Bangladesh}
  \resumeSubHeadingListEnd
  \vspace{-5.5mm}
%-----------PROJECTS-----------------
\section{\textbf{Personal Projects}}
\resumeSubHeadingListStart
    \resumeProject
      {BytesBit | A Computer Retailer Shop}{Github: codesoverign}{Tech: React, Express, Jest, Docker, Tailwind CSS}{}
      \resumeItemListStart
        \item {An online Laptop, Desktop and accessories shop with advance filters and delivery management.}
        \item {Gained experience in Docker containerization and Tailwind CSS.}
        \item {Overcame challenges like how to configure docker compose into a development package using docker volume.}
      \resumeItemListEnd
    \vspace{-2mm}
    \resumeProject
      {Mank | A Tank Brawl Game}{Github: Mank}{Tech: Python, PyOpenGL}{}
      \resumeItemListStart
        \item {A game where user shoots down other tanks in an auto generated maze.}
        \item {Implemented maze algorithm to generate efficient pseudo maze.}
        \item {Learned how using different data structures increase performance for my poor maze drawing algorithm drastically, and handling collision based on object borders while maintaining greater than single pixel displacement.}
      \resumeItemListEnd
    \vspace{-2mm}
    \resumeProject
      {Ultimate Usis Match Finder | A Class Routine Generator}{Github: uumf-py}{Tech: Python, QT, Rest API}{}
      \resumeItemListStart
        \item {A class routine generator can filter routine based on given time or day or faculty or seat number with auto credential login.}
        \item {Was able to perform advising in minutes whereas it took 30 minutes or to do it manually.}
        \item {Automated login by observing browser api calls and simulating them via python session.}
      \resumeItemListEnd
    \vspace{-2mm}
    \resumeProject
      {RedChat | A Basic Encrypted Messaging System}{Github: redchat}{Tech: Django, WebSocket}{}
      \resumeItemListStart
        \item {An end to end encrypted chat system inspired by Jogajog during July Blackout.}
        \item {Made performance improvement with websocket and asynchronous web deployment.}
        \item {In attempt to make it decentralized system via webRTC.}
      \resumeItemListEnd
    \vspace{-2mm}
    \resumeProject
      {BracU Logger | Versity Wifi Logger}{Github: bracu-logger}{Tech: Gradle, Rest API, Java}{}
      \resumeItemListStart
        \item {An app to remember my login credentials and log into wifi with the push of a button.}
        \item {Learned how android GUI structure is Different from web or QT structure.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd
\vspace{-8.5mm}



%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
\begin{itemize}[leftmargin=*,labelsep=0.5em]
  \item 439th at ICPC Regional Preliminary 2021
  \item Linux usage since 2020
  \item Doing Therap Javafest now
\end{itemize}
\vspace{-5.5mm}







%-----------Technical skills-----------------
\section{\textbf{Technical Skills}}
\begin{itemize}[leftmargin=0.05in, label={}]
  \item \textbf{Programming Languages:} Python, C, C++, Java, JavaScript, PHP, SQL, Solidity
  \item \textbf{Web:} HTML5, CSS3, Sass, Tailwind CSS, Bootstrap, React.js, Shadcn, REST API
  \item \textbf{Frameworks/Libraries:} Spring, Django, Qt, Pandas, NumPy
  \item \textbf{Tools:} Docker, Git, GitHub, Bash, Linux, Regex, Web3
  \item \textbf{Other:} Quick learner, passionate coder, app/web/game development, automation
\end{itemize}
\vspace{-16pt}







% %-----------Achievements-----------------
% \section{\textbf{Achievements}}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
    
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
% \resumeSubHeadingListEnd
% \vspace{-5mm}



%-------------------------------------------
\end{document}
