%-----------PROJECTS-----------------

% Projects section only
\section{\textbf{Personal Projects}}
\resumeSubHeadingListStart
    \resumeProject
      {BytesBit | A Computer Retailer Shop}{Github: codesoverign}{Tech: React, Express, Jest, Docker, Tailwind CSS}{}
      \resumeItemListStart
        \item {An online Laptop, Desktop and accessories shop with advance filters and delivery management.}
        \item {Gained experience in Docker containerization and Tailwind CSS.}
        \item {Overcame challenges like how to configure docker compose into a development package using docker volume.}
      \resumeItemListEnd
    \vspace{-2mm}
    \resumeProject
      {Mank | A Tank Brawl Game}{Github: Mank}{Tech: Python, PyOpenGL}{}
      \resumeItemListStart
        \item {A game where user shoots down other tanks in an auto generated maze.}
        \item {Implemented maze algorithm to generate efficient pseudo maze.}
        \item {Learned how using different data structures increase performance for my poor maze drawing algorithm drastically, and handling collision based on object borders while maintaining greater than single pixel displacement.}
      \resumeItemListEnd
    \vspace{-2mm}
    \resumeProject
      {Ultimate Usis Match Finder | A Class Routine Generator}{Github: uumf-py}{Tech: Python, QT, Rest API}{}
      \resumeItemListStart
        \item {A class routine generator can filter routine based on given time or day or faculty or seat number with auto credential login.}
        \item {Was able to perform advising in minutes whereas it took 30 minutes or to do it manually.}
        \item {Automated login by observing browser api calls and simulating them via python session.}
      \resumeItemListEnd
    \vspace{-2mm}
    \resumeProject
      {RedChat | A Basic Encrypted Messaging System}{Github: redchat}{Tech: Django, WebSocket}{}
      \resumeItemListStart
        \item {An end to end encrypted chat system inspired by Jogajog during July Blackout.}
        \item {Made performance improvement with websocket and asynchronous web deployment.}
        \item {In attempt to make it decentralized system via webRTC.}
      \resumeItemListEnd
    \vspace{-2mm}
    \resumeProject
      {BracU Logger | Versity Wifi Logger}{Github: bracu-logger}{Tech: Gradle, Rest API, Java}{}
      \resumeItemListStart
        \item {An app to remember my login credentials and log into wifi with the push of a button.}
        \item {Learned how android GUI structure is Different from web or QT structure.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

